---
title: "A3: SPL Library Checkouts"
output: html_document
---

### Introduction

The dataset that is being analyzed comes from Seattle Open Data which is the city's open data portal. This data was published by City departments available to the public to analyze. I'm choosing to analyze books written by F. Scott Fitzgerald, specifically "The Great Gatsby", as that is my favorite book and I'm interested in whether or not it's other people's favorite book or if other titles such as "The Beautiful and Damned" outshine "The Great Gatsby". 


### Summary Information

From the data, I started to focus more on the author of F. Scott Fitzgerald and the data from having him as an offer. I extracted the maximum number of checkouts which is 76. I also saw when the maximum year of checkouts took place for F. Scott Fitzgerald books which was 2013, but the maximum number of E-Book checkouts is 2023. It reveals that people have been moving away from physical copies of books and towards books read online which makes sense in this day and age with the progression of technology. The minimum amount of total checkouts and E-Book checkouts is 2022 which is interesting because I'm not sure of the significance of that. 


### The Dataset

- Who collected/published the data?  
The data is collected by the City of Seattle and published by the city as well. 

- What are the parameters of the data (dates, number of checkouts, kinds of books, etc.)?
The data was collected between 2005 - 2023 with the kinds of books ranging from Sound Discs, Audio Books, Physical Copies, etc. 

- How was the data collected or generated?  
The data was collected and generated by the City of Seattle through the database that the library uses. 

- Why was the data collected?  
The data was collected for the purpose of "increasing the quality of life for our residents; increasing transparency, accountability and comparability; promoting economic development and research; and improving internal performance management". 

- What, if any, ethical questions do you need to consider when working with this data?  
When working with the data of books, I don't believe there is any ethical questions to consider besides the judgment of the taste of books. 

- What are possible limitations or problems with this data?   (at least 200 words)
The limitations is that humans enter it so there's repetitive data with the books meaning that some of the checkout numbers should be combined. 

### First Trends Over Time Chart

``````{r, echo = FALSE, warning = FALSE, code = readLines("chart1_example.R")}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
From this graph, you are able to see which individual month's total number of checkouts throughout the year. It's evident from the graph that it fluctuates throughout the year, but there's a greater amount of purchases near the summer that ends up decreasing when it gets later during the year. 

### Second Trends Over Time Chart

``````{r, echo = FALSE, code = readLines("chart2_example.R")}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
From this graph, you are able to see the evident trends of material type for Fitzgerald's books and it's very evident that there is a bigger push of physical books rather then audio books which come second in frequency then ebooks. The trends are slightly similar as well with an increase right before the summer then a decrease as summer progresses. The trendline also slightly goes up when school starts again in September. 

### Your Choice

``````{r, echo = FALSE, code = readLines("chart3.R")}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

From this graph, you are able to see the number of total checkouts throughout the years with Books being the greatest -- reaching close to 6,000. Audiobook falls behind going towards 1,000 with SoundDisc coming right below 1,000. EBook comes at around 500 - 600 and song and video are present but they barely contribute to the whole. 
